Analysis Stand Features 

### 2017-05-10 analysis/analysis_stand_features.Rmd
update stand features

## Compute competence index

`TODO` documentar

```{r}
focal_trees <- compete %>% filter(id_core != 'Fresno') 
focal_trees <- unique(focal_trees$id_core)

output<- vector("list", length(focal_trees))

for (i in 1:length(focal_trees)){

# Create df   
df <- compete %>% 
  filter(id_core == focal_trees[[i]])

# Fixed Variables 
radius_plot <- 10 # radius plot (10 m)
sf_plot <- pi * radius_plot^2 # surface plot (m2)
dnft <- filter(df, sp== 'Focal')$dn # normal diameter focal tree    
# ----------

# Competence indices 
## Number of competitors (r = 10)
n_competitors <- filter(df, sp != 'Focal') %>% count()

## Number of competitors with dn_j > dn_i (focal tree)
n_competitors_hihger <- df %>%
  filter(sp != 'Focal') %>%
  filter(dn > dnft) %>% 
  count()

## Plot density (tree/plot)
plot_density <- n_competitors / sf_plot

## Stand density (tree / ha) 
stand_density <- (n_competitors * 10000) / sf_plot

## Sum sizes 
sum_sizes <- df %>% 
  filter(sp != 'Focal') %>%
  summarise(sum_sizes=sum(dn))

## Size ratio 
size_ratio <- dnft / (dnft + sum_sizes$sum_sizes)

## Distance nearest tree
dist_nn <- df %>% 
  filter(sp != 'Focal') %>% 
  slice(which.min(distance_cm))

dist_nn <- (dist_nn$distance_cm / 100)

## Various 
### Basal area
### Size ratio proportional to distance 
### Size difference proportional to distance 
### Negative exponential size ratio
### Negative exponential weighted size ratio
### Lorimer 
### Crowding 
df_more_indices <- df %>%
  filter(sp != 'Focal') %>%
  mutate(
    basal_area = ((pi/4) * dn * dn), 
    size_ratio_distance = (dn / dnft) * (1 / ((distance_cm/100) + 1)),
    size_diff_distance = (dn - dnft) / ((distance_cm/100) + 1),
    neg_exp_size_ratio = (dn / dnft) * (1 / exp((distance_cm/100) + 1)),
    neg_exp_w_size_ratio = (dn / dnft) * exp((-(distance_cm/100) + 1) / (dn + dnft)),
    lorimer = (dn / dnft) / (sqrt((distance_cm/100) / radius_plot)),
    crowding = dn / (distance_cm/100))

df_indices <- df_more_indices %>% 
  summarise(ba = sum(basal_area),
            srd = sum(size_ratio_distance),
            sdd = sum(size_diff_distance),
            nesr = sum(neg_exp_size_ratio),
            newsr = sum(neg_exp_w_size_ratio),
            lorimer = sum(lorimer),
            crowding = sum(crowding)) %>% 
  mutate(nc = n_competitors,
         nch = n_competitors_hihger,
         pd = plot_density,
         std = stand_density,
         ss = sum_sizes,
         sr = size_ratio,
         dnn = dist_nn, 
         id_plot = focal_trees[[i]])

output[[i]] <- df_indices 
}

df_indices_plot <- bind_rows(output)

rm(n_competitors, n_competitors_hihger, plot_density, stand_density, sum_sizes, size_ratio, dist_nn, df, df_indices, output, df_more_indices, dnft)
```

## Plot

```{r}
get_coords_trees <- function(angle, distance, x0, y0) {
  angle <- ifelse(angle <= 90, 90 - angle, 450 - angle)
  data.frame(x = x0 + distance * cos(angle / 180 * pi),
             y = y0+ distance * sin(angle / 180 * pi))
}

compete <- compete %>% 
  mutate(xcord = get_coords_trees(angle= rumbo_degree, 
                           distance = distance_cm/100,
                           x0 = 0, y0 = 0)$x,
         ycord = get_coords_trees(angle = rumbo_degree, 
                           distance = distance_cm/100,
                           x0 = 0, y0 = 0)$y)
```

```{r}
# see stackoverflow questions 6862742
gg_circle <- function(radius, xcenter, ycenter, color='black', fill=NA, ...){
  x <- xcenter + radius*cos(seq(0,pi, length.out = 100))
  ymax <- ycenter + radius*sin(seq(0, pi, length.out = 100))
  ymin <- ycenter + radius*sin(seq(0, -pi, length.out = 100))
  annotate("ribbon", x=x, ymin=ymin, ymax=ymax, color=color, fill=fill, ...)
}

compete %>%  
  filter(sp != 'Focal') %>%
  ggplot(aes(x=xcord, y=ycord)) + 
  facet_wrap(~id_core) + 
  geom_point(aes(size=perim_mm), shape=21, fill='transparent') + 
  xlim(-11,11) + ylim(-11,11) + 
  geom_point(aes(x=0, y=0), color='green') +
  theme_bw() +
  gg_circle(radius = 10, xcenter = 0, ycenter = 0) +
  theme(panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank()) 
```

```{r}

@@

>>>>

# Competition data
```{r}
# Read competition
compe <- read.csv(file=paste(di, "/data/competence/competence_indices.csv", sep=""), header=TRUE, sep=',')

@@

Conclusiones_Taller_EME_SN_borrador_para_devolucion.doc
